Peer influences in air travel behavior: A social autoregressive analysis

### 2015-03-27 article.Rmd
Basic document cleanup.

Candidate Weighting Schema
-----------------------------------------
The social network data we retrieved from Facebook allow us to construct four social weights matrices, which we describe in this section. To aid this presentation, we must first establish some basic notation following elementary set theory. The set of friends of an individual $i$ is defined as $\phi_i$. The cardinality of this set is the number of friends, so therefore the quantity $|\phi_i \cup \phi_j|$ represents the number of friends that individuals $i$ and $j$ have in common.

@@

By Facebook’s internal logic, each of these matrices must be symmetric: it is
not possible on Facebook to have non-reciprocal friends. However, the individual
user privacy settings make it possible that we would observe apparent one-way
relationships through the API; indeed, this affected approximately 10% of cases.
We therefore coerce this and other schema to be symmetric as appropriate.

As a final note on the schema development, behavioral inference on and
estimation of the models is simplified by using a row-standardized matrix, where
the rows sum to unity(LeSage & Pace 2009, p.85). We follow this convention
in all cases.

>>>>

Candidate Weighting Schema
-----------------------------------------
The social network data we retrieved from Facebook allow us to construct at least
four social weights matrices, which we describe in this section. To aid this 
presentation, we must first establish some basic notation following elementary 
set theory. The set of friends of an individual $i$ is defined as $\phi_i$. 
The cardinality of this set is the number of friends, so therefore the quantity 
$|\phi_i \cup \phi_j|$ represents the number of friends that individuals $i$ 
and $j$ have in common.

@@

By Facebook’s internal logic, each of these matrices must be symmetric: it is
not possible on Facebook to have non-reciprocal friends. However, the individual
user privacy settings make it possible that we would observe apparent one-way
relationships through the API; indeed, this affected approximately 10% of cases.
We therefore coerced all schemata to be symmetric as appropriate.

```{r force_symmetric}
# still need to implement
```

As a final note on the schemata development, behavioral inference on and
estimation of the models is simplified by using a row-standardized matrix, where
the rows sum to unity(LeSage & Pace 2009, p.85). We follow this convention
in all cases.

```{r save_as_matrices}

```
